How Significant was WW2 in the Development of the Computer?

### 2017-02-22 Draft 2/Section 3 - Universality.tex
I am literally so tired I have no idea what I changed
Started work on the config getter function and pasted a useless table

\subsubsection{Emulating the Tape}
In order to achieve this, we must define certain new objects in $\lambda$-calculus. First of all, ordered lists - these will be used to describe the current content of the tape. These are defined as a sequence of nodes, where each node is a pair with the first element as the content of the node and the second element is the next node in the sequence. The final node will have \textbf{0} as its first element to signify the end of the list - the second element will never be referred to; as such \textbf{0} will be used as a placeholder (of course this only works if the list is not designed to contain any values of zero or true, as they will be indistinguishable from the end marker - I shall use \textbf{1} to represent $S_0$, \textbf{2} to represent $S_1$ and so on). For example, the list [a,b,c,d,e] would be represented as:
\begin{equation*}
\lambda l.la(\lambda m.mb(\lambda n.nc(\lambda o.od(\lambda p.pe\bm{\mathrm{F}}))))
\end{equation*}
In order to obtain the first element (head), the argument \textbf{T} would be applied to the list; to get the remaining elements (tail) the \textbf{F} argument would be applied. 
Furthermore, to prepend an element to the start of a list:
\begin{equation*}
\bm{\mathrm{:}} = \lambda xlf.f[x][l]
\end{equation*}
This takes an element to prepend $x$, and a list $l$, and constructs a new pair with the given element as the first element and the original list as the second.

@@

Unfortunately, the tape which we are currently dealing with is unlike that of a Turing machine, due to the fact that it is of finite length - we cannot write a single list in $\lambda$-calculus which expresses the entire tape. As such, when the machine moves left or right onto the node with \textbf{0} as the head signifying the end of the list, we will replace it with a node containing the blank square symbol $S_0$, represented by a \textbf{1}, as the head, and another end marker node as he tail. To do this, we will have another transformation function which will check if either head element of the tape pair is \textbf{0}, and if so, will replace it with an empty square node $\bm{\epsilon}$ - otherwise it will simply be replacced with the original head:

@@

\subsubsection{Storing \& Accessing \textit{m}-configurations}
%\subsubsubwithchickenandmayopleasethanks{eating & fulfilling life goals #subwaydatesboiiiiis love man chllz peace wavey donss}
Once again, in order to store the information and operations associated with each \textit{m}-configuration, we shall use another list. The first element of the list shall represent $q_0$, the second $q_1$ and so on.
Each element of the list will be a pair: firstly, the symbol which should be checked for, as a real number; secondly, the transformation that should be performed on the tape. This transformation will be of the form $(\bm{C})(\{\bm{M}_L/\bm{M}_R/\bm{M}_S\})(\bm{W}a)$, which applies first a write transformation first, before a movement transformation and the tape length correction transformation.

>>>>

\subsubsection{Emulating the Tape}
In order to achieve this, we must define certain new objects in $\lambda$-calculus. First of all, ordered lists - these will be used to describe the current content of the tape. These are defined as a sequence of nodes, where each node is a pair with the first element as the content of the node and the second element is the next node in the sequence. The final node will have \textbf{0} as its first element to signify the end of the list - the second element will never be referred to; as such \textbf{0} will be used as a placeholder (of course this only works if the list is not designed to contain any values of zero or true, as they will be indistinguishable from the end marker - I shall use \textbf{1} to represent $S_0$, \textbf{2} to represent $S_1$ and so on). For example, the list [a,b,c,d,e] would be represented as:
\begin{equation*}
\lambda l.la(\lambda m.mb(\lambda n.nc(\lambda o.od(\lambda p.pe(\lambda z.z\bm{\mathrm{00}})))))
\end{equation*}
In order to obtain the first element (head), the argument \textbf{T} would be applied to the list; to get the remaining elements (tail) the \textbf{F} argument would be applied. 
Furthermore, to prepend an element to the start of a list:
\begin{equation*}
\bm{\mathrm{:}} = \lambda xlf.f[x][l]
\end{equation*}
This takes an element to prepend $x$, and a list $l$, and constructs a new pair with the given element as the first element and the original list as the second.

@@

Unfortunately, the tape which we are currently dealing with is unlike that of a Turing machine, due to the fact that it is of finite length - we cannot write a single list in $\lambda$-calculus which expresses the entire tape. As such, when the machine moves left or right onto the node with \textbf{0} as the head signifying the end of the list, we will replace it with a node containing the blank square symbol $S_0$, represented by a \textbf{1}, as the head, and another end marker node as he tail. To do this, we will have another transformation function which will check if either head element of the tape pair is \textbf{0}, and if so, will replace it with an empty square node $\bm{\epsilon}$ - otherwise it will simply be replaced with the original head:

@@

\subsubsection{Storing \& Accessing \textit{m}-configurations}
%\subsubsubwithchickenandmayopleasethanks{eating & fulfilling life goals #subwaydatesboiiiiis love man chllz peace wavey donss}
Once again, in order to store the information and operations associated with each \textit{m}-configuration, we shall use another list. The first element of the list shall represent $q_0$, the second $q_1$ and so on.
Each element of the list will be a list in itself. Each element of this list shall refer to the symbol aspect of the configuration. Each element of the list is a pair: the first element being the symbol to be found (a real number), the second being the actions to be performed under this configuration.

The action itself will be yet another pair. The first element is the transformation that should be performed on the tape - this transformation will be of the form $(\bm{C})(\{\bm{M}_L/\bm{M}_R/\bm{M}_S\})(\bm{W}a)$, which applies first a write transformation before a movement transformation and the tape length correction transformation. The second element is a function which, when given the description of the machine, finds the given \textit{m}-configuration. We shall note these m-configuration references as shown, with the example of the reference to $q_3$:
\begin{equation*}
\bm{Q}_3 = \lambda l.l\bm{\textbf{FFFT}}
\end{equation*}
This gets the fourth head of the given list, which refers to $q_3$.

As an example, here is the description for the first machine described, which generates the sequence \texttt{01010101...} (for clarity, this version does not leave \textit{s}-squares blank). For reference, here is the enumerated table:
%\medskip\noindent\begin{tabu} to \textwidth{XXXX}
%    \multicolumn{2}{c}{\textit{Configuration}} & \multicolumn{2}{c}{\textit{Behavior}} \\
%    \textit{m-config} & \textit{symbol} & \textit{operations} & \textit{final m-config} \\
%    \hhline{====}
%    $q_0$ & $S_0$ & PS_1       & $\mathbb{A}$ \\
%    $q_0$ & $S_1$ & PS_2 & $\mathbb{A}$ \\ 
%    $q_0$ & \texttt{1}    & R, R, P\texttt{0} & $\mathbb{A}$ \\ 
%\end{tabu}
We shall represent this table as such:
\begin{gather*}
\begin{aligned}
\bm{}
\end{aligned}
\end{gather*}
{I cba to do this now}

In order to find which action should be performed given a certain configuration, we shall use the following function which produces a pair of a list transformation and an \textit{m}-config reference from a current \textit{m}-config, the current symbol, and the description function.

\begin{gather*}
\begin{aligned}
\bm{I} = \lambda qsc.(qc)(RECURSIVE FUNCTION TO GET SYMBOL)
\end{aligned}
\end{gather*}
